Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-07 implementation.tex
some rearrangment
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@949 ccdd05d5-56c1-461a-bf98-85f6876523b4

The choice of templates and the \SVD\ can be done in
advance and will be valid as long as the detector noise spectrum remains
roughly constant%
\editorial{I'd rather not go into this.}%
.  New templates and the \SVD\ can be computed asynchronously using
updated spectrum estimates as they are available.

\begin{figure}[htbp]
	\label{fig:tmpltbank}
	\begin{center}
		\includegraphics{figures/tmpltbank.png}
		\caption{Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We shall design a filter bank to search for a small subset of these template parameters with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}

\begin{table}
\begin{indented}
\caption{Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  The \SVD{} tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\item[]\begin{tabular}{rr@{,}lc*{6}{r}}
\br
\multicolumn{4}{c}{} &\centre{6}{$\log_{10}$ (1 - \textsc{svd} tolerance)} \\
\ns
\multicolumn{4}{c}{} &\crule{6} \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & -1 & -2 & -3 & -4 & -5 & -6 \\
\mr
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\br
\end{tabular}
\end{indented}
\end{table}

>>>>

The choice of templates and the \SVD\ can be done in advance.  New templates
and the \SVD\ can be computed asynchronously using updated spectrum estimates
as they are available.
